\begin{rubric}{Miscellaneous Experience}
  \subrubric{Extracurriculars}
  \entry*[Sept 2016 -- present] \textbf{Furche High School Outreach Program} - Irvine, CA.
  \vspace{-0.5em}
   \begin{itemize}
     \itemsep-0.5em
   \item Led the outreach program to provide research opportunities for underserved communities
     throughout the United States; created a community with 18 high school students and
     10 graduate mentors
   \item Volunteered 5000+ hours and co-authored research grants to support the program
   \vspace{-1em}
   \end{itemize}
%
   \entry*[Jun 2017 -- Sept 2017] \textbf{UCI Competitive Edge Peer Mentor} - Irvine, CA.
   \vspace{-0.5em}
   \begin{itemize}
   \itemsep-0.5em
   \item Welcomed incoming UCI doctoral students for smooth transition into graduate school
   \item Provided weekly one-on-one individual meetings for mentees to discuss research, presentation
     skills, and fellowship applications
   \vspace{-1em}
   \end{itemize}
%   
\entry*[Sept 2016 -- Feb 2020] \textbf{Orange County Regional Science Olympiad} - Irvine, CA.
\vspace{-0.5em}
   \begin{itemize}
   \itemsep-0.5em
   \item Created and standardized 8 experimental design exams for middle and high school students in
     2017, 2018, 2019, and 2020 OC Regional Science Olympiad at UCI
   \item Mentored and taught an undergraduate to design and proctor the experimental design exam
   \vspace{-1em}
   \end{itemize}
%
\subrubric{Awards and Achievements}
\entry*[Jun 2021] \textbf{UCI School of Physical Sciences Faculty Endowed Fellowship},

University of California, Irvine.
%
\entry*[Jun 2021] \textbf{UCI Dissertation Fellowship in Chemistry},

University of California, Irvine
%
\entry*[Sept 2016] \textbf{UCI Graduate Chancellor Fellowship in Chemistry},

University of California, Irvine.
%
\entry*[Jun 2015] \textbf{UCI Chancellor's Undergraduate Award of Distinction},

University of California, Irvine.
%
\entry*[May 2015] \textbf{Phi Beta Kappa}.
%
\entry*[May 2015] \textbf{Phi Lambda Upsilon}.
%
\entry*[Jun 2014] \textbf{Hypercube Scholar Award},

Hypercube Inc.
%
\entry*[Apr 2014] \textbf{OC American Chemical Society Undergraduate Award},

Orange County American Chemical Society Local Chapter.
%
\subrubric{Certifications}
\entry*[Mar 2020] \textbf{UCI Graduate Division Mentoring Excellence Program}
%
\entry*[Jun 2017] \textbf{UCI GPS-BIOMED Effective Communication Program} 
\end{rubric}
