\documentclass[letterpaper,11pt]{article}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\def\name{Brian D. Nguyen}
\def\footerlink{}
%==============================================================================%
%                            Metadata for pdf
%==============================================================================%
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}
\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}
%==============================================================================%
%                               Page Headers
%==============================================================================%
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}
%==============================================================================%
%                               Section Fonts
%==============================================================================%
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
\subsectionfont{\rmfamily\bfseries}
\setlength\parindent{0pt}
%==============================================================================%
%                            List Without Bullets
%==============================================================================%
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}
%==============================================================================%
%                             Begin Document
%==============================================================================%
\begin{document}
\centerline{\huge \textbf{\name}}
\vspace{0.2in}
%==============================================================================%
%                          University Affiliation
%==============================================================================%
University of California, Irvine\hfill bdnguye2@uci.edu\\
Department of Chemistry \hfill \href{www.linkedin.com/in/brian-nguyen-8262a3104}{Linkedin}\\
1102 Natural Sciences 2\hfill 714-204-6033\\
Irvine, CA 92697-2025\\

%California Institute of Technology, Pasadena\hfill sflynn@caltech.edu\\
%Department of Chemistry and Chemical Engineering\hfill shane.flynn001@gmail.com\\
%316 Beckman Institute \hfill 413-841-5470\\
%Pasadena, CA 91125\\

%University of Massachusetts Boston, Boston\hfill shane.flynn001@umb.edu\\
%Department of Chemistry, Biology, Mathematics \hfill shane.flynn001@gmail.com\\
%ISC-3700\hfill 413-841-5470\\
%Boston, MA 02125-3393\\

\vspace{0.2in}
\hrule

%==============================================================================%
%                                  Education
%==============================================================================%
\section*{Education}

\begin{itemize}
    \item \textbf{Ph.D  Chemistry (Anticipated May 2022)}  \hfill 2016-Present\\
      Advisor: Filipp Furche\\
      University of California, Irvine

\item \textbf{B.S. Chemistry, B.S. Biology}
      \hfill 2011-2015\\
      University of California, Irvine
\end{itemize}

\vspace{0.1in}
\hrule
%==============================================================================%
%                               Publications
%==============================================================================%
\subsection*{Publications}

\begin{enumerate}
\item \textbf{Nguyen, B.D.}$^\dagger$; Hernandez, D.J.$^\dagger$;
  Flores, E.; Furche, F. Dispersion Size-Consistency. \textit{Under Review.}
  \textbf{2021}.

\item \textbf{Nguyen, B.D.}$^\dagger$; Yu, J.M.$^\dagger$; Tsai, J.;
  Furche, F. Selfconsistent Random Phase Approximation Methods.
  \textit{J. Chem. Phys.} \textbf{2021}, \textit{155}(4), 040902.

\item Darago, L.E.; Boshart, M.D.; \textbf{Nguyen, B. D.}; Perlt, E.;
  Ziller, J.W.; Lukens, W.W.; Furche, F.; Evans, W.J.; Long, J.R.
  Strong Ferromagnetic Exchange Coupling and Single-Molecule Magnetism in
  MoS$_4^{3-}$-Bridged Dilanthanide Complexes. \textit{J. Am. Chem. Soc.}
  \textbf{2021}, \textit{143}(22), 8465--8475.

\item Balasubramani, S.G.; [and 36 others, including \textbf{Nguyen, B.D.}]
  TURBOMOLE: Modular Program Suite for Ab Initio Quantum-Chemical and Condensed-Matter
  Simulations. \textit{J. Chem. Phys.} \textbf{2020}, \textit{152}(18), 184017.
      
\item \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Tang, M.P.;
  Furche, F. Divergence of Many-Body Perturbation Theory for Noncovalent Interactions
  of Large Molecules. \textit{J. Chem. Theory Comput.} \textbf{2020}, \textit{16}(4),
  2258--2273.

\item \textbf{Nguyen, B.D.}$^\dagger$; Hollingsworth, S.A.$^\dagger$; Chreifi, G.;
  Arce, A.P.; Poulos, T.L. Insights into the Dynamics and Dissociation Mechanism
  of a Protein Redox Complex Using Molecular Dynamics. \textit{J. Chem. Info. Model.}
  \textbf{2017}, \textit{57}(9), 2344--2350.

\item Steinhardt, R. C.; Rathbun, C.M.; Krull, B.T.; Yu, J.M.; Yang, Y.;
  \textbf{Nguyen, B.D.}; Kwon, J.; McCutcheon, D.C.; Jones, K.A.; Furche, F.;
  Prescher, J. A. Brominated Luciferins Are Versatile Bioluminescent Probes.
  \textit{ChemBioChem} \textbf{2016}, \textit{18}(1), 96--100.

\item Hollingsworth, S. A.$^\dagger$; Batabyal, D.$^\dagger$; \textbf{Nguyen, B. D.};
  Poulos, T. L. Conformational Selectivity in Cytochrome P450 Redox Partner
  Interactions. \textit{Proc. Natl. Acad. Sci.} \textbf{2016}, \textit{113}(31),
  8723--8728.

\item Furche, F.; Krull, B.T.; \textbf{Nguyen, B.D.}; Kwon, J. Accelerating
  Molecular Property Calculations with Nonorthonormal Krylov Space Methods.
  \textit{J. Chem. Phys.} \textbf{2016}, \textit{144}(17), 174105. 

\end{enumerate}

$\dagger$ Indicates that authors contributed equally

\vspace{0.1in}
\hrule

%==============================================================================%
%                             Research Positions
%==============================================================================%
\section*{Research Experience}

\begin{itemize}
\item \textbf{Graduate Researcher, Chemistry}\hfill 2017-Present\\
  University of California, Irvine\\
  Advisor: Filipp Furche \\
  Research: Understanding the behavior of noncovalent interactions, and
  mentoring 15 high school and 4 undergraduate students.

\item \textbf{Undergraduate Researcher, Mathematics}\hfill Summer 2016\\
  University of California, Irvine \\
  Advisor: Frederic Y. Wan\\
  Research: Developed mathematical model of the early development of
  fruit fly.
  
\item \textbf{Undergraduate Researcher, Biology}\hfill 2014-2016\\
  University of California, Irvine \\
  Advisor: Thomas L. Poulos \\
  Research: Simulated mechanism of \textit{Leishmania major} peroxidase,
  and predicted the dominant protein conformation of cytochrome P450.

\item \textbf{Undergraduate Researcher, Chemistry}\hfill 2013-2016\\
  University of California, Irvine\\
  Advisor: Filipp Furche \\
  Research: Developed luciferin derivatives for bioluminescence, and
  improved molecular property calculations for TURBOMOLE quantum package.
\end{itemize}

\vspace{0.1in}
\hrule
%==============================================================================%
%                             Research Positions
%==============================================================================%

\subsection*{Selected Poster Presentations}

\begin{itemize}

\item \textbf{2020 Fall ACS National Meeting \& Expo}, \textit{San Francisco}, Poster. \\
  \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Tang, M.P.;
  Furche, F. Divergence of Many-Body Perturbation Theory, April \textbf{2020},

\item \textbf{2019 Southern California Theoretical Chemistry Symposium}, \textit{Los Angeles}, Poster. \\
  \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Furche, F.  
  Size dependence of noncovalent interactions within RPA, May \textbf{2019}

\end{itemize}

\vspace{0.1in}
\hrule

\end{document}
