%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.

%
% Creator Peilin Li
% Contact me via twitter/wechat: @pe1l1nl1
% linkedin.com/peill and/or github/ppeill
% Inspired by Peppa Pig 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.2in,right=0.4in,bottom=0.2in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\usepackage{multicol}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\name{Brian D. Nguyen} % Your name 

%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\faLink{\href{www.linkedin.com/in/brian-nguyen-8262a3104}{\,LinkedIn: brian-nguyen}} \,\,
  \faEnvelope{\,bdnguye2@uci.edu}\,\, \faMapMarker{\,Irvine, California}\,\, \faPhone\,(714) 204-6033} % Your address

\begin{document}
{\centerline { } }
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.3in}

\begin{rSection}{Education}

{\bf University of California, Irvine} \hfill {\em Sept 2016 - expected May 2022} 
\\{\textit{Ph.D. in Chemistry with concentration in Chemical and Materials Physics}}

{\bf University of California, Irvine} \hfill {\em Sept 2011 - Mar 2015} 
\\ { \textit{B.S. Chemistry, cum laude}} \& {\textit{B.S. Biology, cum laude}} \hfill

\end{rSection}

\begin{rSection}{Research Experience}

\textbf{Graduate Researcher, Chemistry} - University of California, Irvine \hfill {\em Sept 2016 - present}\\
Advisor: Filipp Furche
\vspace{-0.5em}
\begin{itemize}    
\itemsep-0.65em
\item Developed theories and models to predict the behavior of noncovalent interactions
\item Initiated cancer drug collaboration with the Vanderwal Lab at UCI and developed model of
  the \\
  $\sim$200,000 atoms protein-drug complex leading to potential drug candidates; publication \textit{in prep}
\item Collaborated with the Long Group at UC Berkeley and developed model to understand the electronic \\
  structure of dilanthanide single molecule magnets; published in \textit{J. Am. Chem. Soc.}
\end{itemize}

\end{rSection}

\begin{rSection}{Work Experience}
  
  {\bf Morpho Detection, LLC} - Santa Ana, CA \hfill {\em Dec 2015 - Jun 2016}  \\
  {\textit{Chemist Intern}}
  \vspace{-0.5em}
  \begin{itemize}
  \itemsep-0.75em
  \item Tested the accuracy of mass spectrometry device for bomb detection and communicated
    with senior\\
    scientists on the development of the devices
  \item Calibrated and tested the bomb detection accuracy of the devices for
    government certification
  \end{itemize}  

\end{rSection}

\begin{rSection}{Selected Publications}

  \textit{Selected publications from 8 published, 1 under review and
    2 in preparation};  
  $*$ Indicates that authors contributed equally
  
\begin{enumerate}
\item \textbf{Nguyen, B.D.}$^*$; Hernandez, D.J.$^*$;
  Flores, E.; Furche, F. Dispersion Size-Consistency. \textit{Accepted.}
  \textbf{2021}.

\item {\em Editor's Pick} - \textbf{Nguyen, B.D.}$^*$; Yu, J.M.$^*$; Tsai, J.;
  Furche, F. Selfconsistent Random Phase Approximation Methods.
  \textit{J. Chem. Phys.} \textbf{2021}, \textit{155}(4), 040902.
      
\item \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Tang, M.P.;
  Furche, F. Divergence of Many-Body Perturbation Theory for Noncovalent Interactions
  of Large Molecules. \textit{J. Chem. Theory Comput.} \textbf{2020}, \textit{16}(4),
  2258--2273.

\item \textbf{Nguyen, B.D.}$^*$; Hollingsworth, S.A.$^*$; Chreifi, G.;
  Arce, A.P.; Poulos, T.L. Insights into the Dynamics and Dissociation Mechanism
  of a Protein Redox Complex Using Molecular Dynamics. \textit{J. Chem. Info. Model.}
  \textbf{2017}, \textit{57}(9), 2344--2350.
  
\end{enumerate}

\end{rSection}

\begin{rSection}{Selected Presentations}

\textit{Selected presentations from 6 conferences}

  \begin{enumerate}

  \item \textbf{2022 Spring ACS National Meeting \& Expo}, San Francisco, CA - \textit{accepted} Oral. \\
  \textbf{Nguyen, B.D.}; Hernandez, D.J.; Flores, E.V.; Furche, F.
  Dispersion Size Consistency, March \textbf{2022}.
    
  \item \textbf{2020 Fall ACS National Meeting \& Expo}, San Francisco, CA - Poster. \\
  \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Tang, M.P.;
  Furche, F. Divergence of Many-Body Perturbation Theory, April \textbf{2020}.

  \end{enumerate}
  
\end{rSection}

\begin{rSection}{Selected Extracurriculars}

  {\bf Furche High School Outreach Program} - Irvine, CA \hfill {\em Sept 2016 - present} \\
  {\textit{Program Coordinator}}
  \vspace{-0.5em}
  \begin{itemize}
    \itemsep-0.75em
  \item Led the outreach program to provide research opportunities for underserved communities
    throughout \\
    the United States; created a community with 18 high school students and 10 graduate mentors
  \item Volunteered 5000+ hours and co-authored research grants to support the program
  \end{itemize}

\end{rSection}

\begin{rSection}{Selected Awards and Honors}
  UCI School of Physical Sciences Faculty Endowed Fellowship \hfill {\em Jun 2021} \\
%  UCI Dissertation Fellowship \hfill {\em Jun 2021} \\
%  UCI Chancellor's Fellowship in Chemistry \hfill {\em Apr 2016} \\
  UCI Chancellor's Undergraduate Award of Distinction \hfill {\em Jun 2015} \\
  Phi Beta Kappa \hfill {\em May 2015} \\
  Phi Lambda Upsilon \hfill {\em May 2015} \\
  Hypercube Scholar Award \hfill {\em Jun 2014} \\
  OC American Chemical Society Undergraduate Award \hfill {\em Apr 2014}
\end{rSection}

\end{document}
