%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.

%
% Creator Peilin Li
% Contact me via twitter/wechat: @pe1l1nl1
% linkedin.com/peill and/or github/ppeill
% Inspired by Peppa Pig 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\usepackage{multicol}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\name{Brian D. Nguyen} % Your name 

%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\faLink{\href{www.linkedin.com/in/brian-nguyen-8262a3104}{\,LinkedIn: brian-nguyen}} \,\,
  \faEnvelope{\,bdnguye2@uci.edu}\,\, \faMapMarker{\,Irvine, California}\,\, \faPhone\,(714) 204-6033} % Your address

\begin{document}
{\centerline { } }
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.3in}
\begin{rSection}{Objective}
  
  8+ years experience in computational and theoretical chemistry research and education.
  Seeking a senior research and development position in molecular modeling to develop new
  materials. 

\end{rSection}

\begin{rSection}{Education}

{\bf University of California, Irvine} \hfill {\em Sept 2016 - expected May 2022} 
\\{\textit{Ph.D. in Chemistry \\
    with concentration in Chemical and Materials Physics}}

{\bf University of California, Irvine} \hfill {\em Sept 2011 - Mar 2015} 
\\ { \textit{B.S. Chemistry, cum laude}} \hfill
\\ { \textit{B.S. Biology, cum laude}} \hfill

\end{rSection}

\begin{rSection}{Research Experience}

\textbf{Graduate Researcher, Chemistry}\hfill {\em Sept 2016 - present}\\
University of California, Irvine\\
Advisor: Filipp Furche
\vspace{-0.5em}
\begin{itemize}    
\itemsep-0.65em
\item Developed theories and models to predict the behavior of noncovalent interactions (NI)
\item Initiated collaboration with the Vanderwal Lab at UCI leveraging knowledge in NIs to improve\\
  the efficacy of cancer drugs; publication \textit{in prep}
\item Collaborated with the Long Group at UC Berkeley and developed model to understand the electronic \\
  structure of dilanthanide single molecule magnets; published in \textit{J. Am. Chem. Soc.}
\item Provided weekly one-on-one research mentorship for 4 undergraduates %(Emily, Poorvi, Devin, and Emmanuel)
  and 4 high school students %(Matthew, Jenny, Thanh, and Natalie)
\item 1 undergraduate pursued Chemical Engineering Ph.D. program at Columbia University and
  4 high \\
  school students pursued biology, earth system science, and chemistry majors at UCI
  and UCSB
\end{itemize}

\textbf{Undergraduate Researcher, Mathematics}\hfill {\em Jun 2016 - Sept 2016}\\
University of California, Irvine \\
Advisor: Frederic Y. Wan
\vspace{-0.5em}
\begin{itemize}
\itemsep-0.65em
\item 1 of 20 students accepted into the Mathematical and Computational Biology for Undergraduate \\
  summer program
\item Collaborated with mathematician to develop a mathematical model that predicted the early \\
  development of fruit flies matching experimental studies
\end{itemize}
  
\textbf{Undergraduate Researcher, Biology}\hfill {\em Mar 2014 - Jun 2016}\\
University of California, Irvine \\
Advisor: Thomas L. Poulos
\vspace{-0.5em}
\begin{itemize}
\itemsep-0.65em
\item Simulated and predicted the mechanism of \textit{Leishmania major} peroxidase through
  molecular \\
  dynamics (MD) simulations; results supported experiments and published in \textit{J. Chem. Info. Model.}
\item Predicted the dominant protein conformation of cytochrome P450 through
  MD simulations \\
  matching experiments; published in \textit{PNAS}
\end{itemize}

\textbf{Undergraduate Researcher, Chemistry}\hfill {\em Oct 2013 - Jun 2016}\\
University of California, Irvine\\
Advisor: Filipp Furche
\vspace{-0.5em}
\begin{itemize}
\itemsep-0.65em
\item Collaborated with Prescher Lab to produce luciferin derivatives that emit
  $\sim$2x stronger signal for\\
  bioluminescence; published in \textit{ChemBioChem}
\item Developed up to $\sim$4x faster algorithm for molecular property calculations and coded
  within the \\
  TURBOMOLE quantum package; published in \textit{J. Chem. Phys.}
\end{itemize}

\end{rSection}

\begin{rSection}{Work Experience}
  
  {\bf University of California, Irvine} - Irvine, CA \hfill {\em Jan 2019 -- Mar 2019} \\
  \textit{Graduate Chemistry Teacher Assistant}
  \vspace{-0.5em}
  \begin{itemize}
    \itemsep-0.5em
  \item Taught for two graduate level chemistry courses:
    Chem 254 - Computational Chemistry \\
    and Chem 232B - Quantum Mechanics
  \item Led discussion and lab sections for over 40 students
  \end{itemize}
\pagebreak
  {\bf University of California, Irvine} - Irvine, CA \hfill {\em Sept 2016 -- Jun 2017} \\
  \textit{Undergraduate Chemistry Teacher Assistant}
  \vspace{-0.5em}
  \begin{itemize}
  \itemsep-0.5em
  \item Taught for general chemistry lecture and lab courses (Chem M2LA/H2LA,
    Chem 1B, and Chem 1C)
  \item Led discussion and lab sections for over 200 students
  \end{itemize}
  
  {\bf Morpho Detection, LLC} - Santa Ana, CA \hfill {\em Dec 2015 - Jun 2016}  \\
  {\textit{Chemist Intern}}
  \vspace{-0.5em}
  \begin{itemize}
  \itemsep-0.75em
  \item Tested the accuracy of mass spectrometry device for bomb detection and communicated
    with senior\\
    scientists on the development of the devices
  \item Calibrated and tested the bomb detection accuracy of the devices for
    government certification
  \end{itemize}  

\end{rSection}

\begin{rSection}{Selected Publications}

  \textit{Selected publications from 8 published, 1 under review and
    2 in preparation};  
  $*$ Indicates that authors contributed equally
  
\begin{enumerate}
\item \textbf{Nguyen, B.D.}$^*$; Hernandez, D.J.$^*$;
  Flores, E.; Furche, F. Dispersion Size-Consistency. \textit{Under Review.}
  \textbf{2021}.

\item {\em Editor's Pick} - \textbf{Nguyen, B.D.}$^*$; Yu, J.M.$^*$; Tsai, J.;
  Furche, F. Selfconsistent Random Phase Approximation Methods.
  \textit{J. Chem. Phys.} \textbf{2021}, \textit{155}(4), 040902.

%\item Darago, L.E.; Boshart, M.D.; \textbf{Nguyen, B. D.}; Perlt, E.;
%  Ziller, J.W.; Lukens, W.W.; Furche, F.; Evans, W.J.; Long, J.R.
%  Strong Ferromagnetic Exchange Coupling and Single-Molecule Magnetism in
%  MoS$_4^{3-}$-Bridged Dilanthanide Complexes. \textit{J. Am. Chem. Soc.}
%  \textbf{2021}, \textit{143}(22), 8465--8475.
%
%\item Balasubramani, S.G.; [and 36 others, including \textbf{Nguyen, B.D.}]
%  TURBOMOLE: Modular Program Suite for Ab Initio Quantum-Chemical and Condensed-Matter
%  Simulations. \textit{J. Chem. Phys.} \textbf{2020}, \textit{152}(18), 184017.
      
\item \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Tang, M.P.;
  Furche, F. Divergence of Many-Body Perturbation Theory for Noncovalent Interactions
  of Large Molecules. \textit{J. Chem. Theory Comput.} \textbf{2020}, \textit{16}(4),
  2258--2273.

\item \textbf{Nguyen, B.D.}$^*$; Hollingsworth, S.A.$^*$; Chreifi, G.;
  Arce, A.P.; Poulos, T.L. Insights into the Dynamics and Dissociation Mechanism
  of a Protein Redox Complex Using Molecular Dynamics. \textit{J. Chem. Info. Model.}
  \textbf{2017}, \textit{57}(9), 2344--2350.

%\item Steinhardt, R. C.; [and 8 others, including
%  \textbf{Nguyen, B.D.}] Brominated Luciferins Are Versatile Bioluminescent Probes.
%  \textit{ChemBioChem} \textbf{2016}, \textit{18}(1), 96--100.
%
%\item Hollingsworth, S. A.$^*$; Batabyal, D.$^*$; \textbf{Nguyen, B. D.};
%  Poulos, T. L. Conformational Selectivity in Cytochrome P450 Redox Partner
%  Interactions. \textit{Proc. Natl. Acad. Sci.} \textbf{2016}, \textit{113}(31),
%  8723--8728.
%
%\item Furche, F.; Krull, B.T.; \textbf{Nguyen, B.D.}; Kwon, J. Accelerating
%  Molecular Property Calculations with Nonorthonormal Krylov Space Methods.
%  \textit{J. Chem. Phys.} \textbf{2016}, \textit{144}(17), 174105.
  
\end{enumerate}

\end{rSection}

\begin{rSection}{Selected Presentations}

\textit{Selected presentations from 6 conferences}

  \begin{enumerate}

  \item \textbf{2022 Spring ACS National Meeting \& Expo}, San Francisco, CA - \textit{accepted} Oral. \\
  \textbf{Nguyen, B.D.}; Hernandez, D.J.; Flores, E.V.; Furche, F.
  Dispersion Size Consistency, March \textbf{2022}.
    
  \item \textbf{2020 Fall ACS National Meeting \& Expo}, San Francisco, CA - Poster. \\
  \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Tang, M.P.;
  Furche, F. Divergence of Many-Body Perturbation Theory, April \textbf{2020}.
  
  \item \textbf{2019 Southern California Theoretical Chemistry Symposium}, Los Angeles, CA - Poster. \\
  \textbf{Nguyen, B.D.}; Chen, G.P.; Agee, M.M.; Burow, A.M.; Furche, F.  
  Size dependence of noncovalent interactions within RPA, May \textbf{2019}.
  \end{enumerate}
  
\end{rSection}

\begin{rSection}{Selected Extracurriculars}

  {\bf Furche High School Outreach Program} - Irvine, CA \hfill {\em Sept 2016 - present} \\
  {\textit{Program Coordinator}}
  \vspace{-0.5em}
  \begin{itemize}
    \itemsep-0.75em
  \item Led the outreach program to provide research opportunities for underserved communities
    throughout \\
    the United States; created a community with 18 high school students and 10 graduate mentors
  \item Volunteered 5000+ hours and co-authored research grants to support the program
  \end{itemize}
%  - Mentored 4 high school students (Matthew, Jenny, Thanh, and Natalie) and co-authored papers with them

  {\bf Orange County Regional Science Olympiad} - Irvine, CA \hfill {\em Sept 2016 - Feb 2020}  \\
  {\textit{Proctor and Test Writer}}
  \vspace{-0.5em}
  \begin{itemize}
  \itemsep-0.75em
  \item Created and standardized 8 experimental design exams for middle and high school students in
    2017, \\
    2018, 2019, and 2020 OC Regional Science Olympiad at UCI
  \item Mentored and taught an undergraduate to design and proctor the experimental design exam
    %Gabriel
  \end{itemize}

\end{rSection}

\begin{rSection}{Selected Awards and Honors}
  UCI School of Physical Sciences Faculty Endowed Fellowship \hfill {\em Jun 2021} \\
%  UCI Dissertation Fellowship \hfill {\em Jun 2021} \\
%  UCI Chancellor's Fellowship in Chemistry \hfill {\em Apr 2016} \\
  UCI Chancellor's Undergraduate Award of Distinction \hfill {\em Jun 2015} \\
  Phi Beta Kappa \hfill {\em May 2015} \\
  Phi Lambda Upsilon \hfill {\em May 2015} \\
  Hypercube Scholar Award \hfill {\em Jun 2014} \\
  OC American Chemical Society Undergraduate Award \hfill {\em Apr 2014}
\end{rSection}

\begin{rSection}{Programming Skills}
  \begin{multicols}{6}
    \begin{itemize}
    \setlength\itemsep{-0.75em}
    \item C++  
    \item Python
    \item MATLAB
    \item R
    \item Fortran
    \item Bash
    \end{itemize}
  \end{multicols}
    
\end{rSection}

%\begin{rSection}{Certificates}
%  UCI Graduate Division Mentoring Excellence Program \hfill {\em Mar 2020} \\
%  UCI GPS-BIOMED Effective Communication Program \hfill {\em Jun 2017}
%\end{rSection}

\end{document}
